# Submit Multiple Independent Jobs {#chap-array-jobs-slurm-r}

```{r}
#| results: "asis"
#| echo: false
source("../_common.R")
```

**Note:** This technique was developed to submit jobs to the cluster due to the job array being disabled long ago. With the switch to Slurm, the job array built-in feature has been activated. For details on how to use the built-in Slurm job array, please see @chap-array-jobs-slurm-r.

## Problem statement

Consider the need to obtain random numbers across varying sample sizes and means.

$$N = \begin{cases}
250 \\
500 \\
750 
\end{cases}, \mu = \begin{cases}
0 \\
1.5
\end{cases}$$

## Sample Job script

**sim_job.R**

```{r}
#| echo: false
#| results: "asis"
print_r("scripts/sim_job.R")
```

Download a copy onto the cluster with:

``` bash
wget https://hpc.thecoatlessprofessor.com/slurm/scripts/sim_job.R

chmod +x sim_job.R
```

## Sample Parameter Inputs

**inputs.txt**

```{r}
#| echo: false
#| results: "asis"
print_sh("scripts/inputs.txt")
```

Download a copy onto the cluster with:

``` bash
wget https://hpc.thecoatlessprofessor.com/slurm/scripts/inputs.txt
```

**Note:** Parameters are best generated using `expand.grid()`.

``` r
N_vals = c(250, 500, 750)
mu_vals = c(0, 1.5)

sim_frame = expand.grid(N = N_vals, mu = mu_vals)
sim_frame
# 250 0.0
# 500 0.0
# 750 0.0
# 250 1.5
# 500 1.5
# 750 1.5
```

Write the simulation parameter configuration to `inputs.txt` with:

``` r
write.table(sim_frame, file = "inputs.txt", 
            col.names = FALSE, row.names = FALSE)
```

## Faux Job Array Script

```{r}
#| echo: false
#| results: "asis"
print_sh("scripts/job_builder.sh")
```

Download a copy and run on the cluster with:

``` bash
# Download a copy
wget https://hpc.thecoatlessprofessor.com/slurm/scripts/job_builder.sh

# Enable the script to run.
chmod +x job_builder.sh

# Submit jobs to the queue
./job_builder.sh
```
